---
title: "HW2"
author: "Zhuodiao Kuang"
date: "`r Sys.Date()`"
output: github_document
---




# Problem 1

#### a) What is the probability that exactly 40 of these individuals will have at least one dental checkup?

Let X denote an individual in the study.

Let Y denote the number of individuals who will have at least one dental checkup during a 2-year period.

$$X \sim Bernoulli(0.73) $$

$$Y \sim Bin(56, 0.73), n=56, p=0.73$$

$$P(Y = 40) = \frac{56!}{40!16!}(0.73)^{40}(0.27)^{16}$$
$$ \approx 0.1133$$



#### b) What is the probability that at least 40 of these individuals will have at least one dental checkup?

Let X denote an individual in the study.

Let Y denote the number of individuals who will have at least one dental checkup during a 2-year period.



$$P(Y \ge 40) =\Sigma_{y=40}^{56} \frac{56!}{y!(56-y)!}(0.73)^{y}(0.27)^{1-y}$$

```{r}
P=0
for (y in 40:56) {
  P = P + choose(56,y)*(0.73)^y*(0.27)^(56-y)
}
P
```

So, the probability is about 0.6678.

#### c) Could you use an approximation method to calculate the probabilities above? If yes, calculate the probabilities using approximations and compare to exact values; otherwise, explain why approximation methods are not appropriate.

Approximation methods are not appropriate. we cam only use the Poisson distribution to approximate the binomial distribution under certain conditions, where $\lambda = np$.
1. n must be large(>100)
2. Probability of success, p, should be small(p<0.01)

But this problem doesn't satisfy these conditions.

#### d) How many individuals do you expect to have at least one dental checkup?

$$E(Y) = np = 56*0.73 = 40.88$$
So, I expect 41 individuals to have at least one dental checkup.


#### e) What is the standard deviation of the number of individuals who will have at least one dental checkup?

$$Var(Y) = np(1-p) = 56*0.73*0.27 = 11.0376$$
$$std(Y) = \sqrt{Var(Y)} = 3.322$$

So, the standard deviation of the number of individuals who will have at least one dental checkup is 3.322.

# Problem 2 


#### a) What is the probability of having fewer than 3 tornadoes in the United States next year?

The probability distribution of a Poisson random variable $X \sim Poi(6)$ is denoted by: 

$$P(X=x) = f(x) = \frac{6^xe^{-6}}{x!}, x=0,1,2,...$$
Calculate: 
$$P(X < 3 ) = \Sigma_{x=0}^2\frac{6^xe^{-6}}{x!} $$

$$= \frac{6^0e^{-6}}{0!}+\frac{6^1e^{-6}}{1!}+\frac{6^2e^{-6}}{2!}$$

$$=25e^{-6} \approx 0.062$$

#### b) What is the probability of having exactly 3 tornadoes in the United States next year?

Calculate: 
$$P(X = 3 ) = \frac{6^3e^{-6}}{3!} $$

$$=36e^{-6} \approx 0.089$$


#### c) What is the probability of having more than 3 tornadoes in the United States next year?


$$P(X>3) = 1-P(X \le 3) =1 - 61e^{-6} \approx 0.8488$$

# Problem 3



#### a) What is the probability that a randomly selected American male between 20 and 29 years old has a systolic blood pressure above 137.0?

Let X denote the systolic blood pressure of 20-29 year old American males. 

$$X \sim N(128,(10.2)^2)$$

$$z = \frac{x-\mu}{\sigma} = \frac{137.0-128.0}{10.2} = 0.8824$$
$$P(X>137) = 1-\Phi(z)=0.1889$$

#### b) What is the probability that the sample mean for blood pressure of 50 males between 20 and 29 years old will be less than 125.0?

$$T = \bar{X} = (X_1+...+X_{50})/50$$
Because $X_i, i=1,...50$ are independent, $\bar{X}$ is still normally distributed.

$$E(\bar{X}) = E(X) = 128$$
$$Var(\bar{X}) = \frac{Var(X)}{n} = 2.0808$$
So, $\bar{X} \sim N(128,2.0808)$

$$z = \frac{t-\mu}{\sigma} = \frac{125-128.0}{1.4425} = -2.08$$


$$P(\bar{X}<125) = \Phi(z)=0.0188$$


#### c) What is the 90th percentile of the sampling distribution of the sample mean X for a sample size of 40?



$$Y = \bar{X} = (X_1+...+X_{40})/40$$
Because $X_i, i=1,...40$ are independent, $\bar{X}$ is still normally distributed.

$$E(\bar{X}) = E(X) = 128$$
$$Var(\bar{X}) = \frac{Var(X)}{n} = 2.601$$
So, $\bar{X} \sim N(128,2.601)$

$$z_{0.9} = \frac{y-\mu}{\sigma} = \frac{y-128.0}{1.6128} = 1.2816$$

$$y = 130.0669$$

**Verify:**

```{r}
qnorm(0.9,128,1.6128)
```

This means that there is a 90% chance that the sample mean of 40 randomly selected American males between 20 and 29 years old will be less than or equal to 130.0669 mm Hg.

